Helmet Foam Case Study Report

### 2024-04-30 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd

|    Stiffness Model Predictors    |        Damping Model Predictors                     
|:---------------------------------|:------------------------------------|
            porosity               |             porosity
           chemIndex               |             chemIndex
           log(cycle)              |               freq
       porosity:chemIndex          |             log(cycle)
       chemIndex:log(cycle)        |          porosity:log(cycle)
       porosity:log(cycle)         |         chemIndex:log(cycle)
  porosity:chemIndex:log(cycle)    |            freq:log(cycle)

@@

Level 1: $\log(\text{stiffnessFrac}) = \alpha_i + \beta_i*log(cycle)$
Level 2: $\alpha_i = \alpha_0 + \alpha_1*\text{porosity} + \alpha_2*\text{chemIndex} + \alpha_3*\text{freq} + \alpha_4*\text{amp}$
         $\beta_i = \beta_0 + \beta_1*\text{porosity} + \beta_2*\text{chemIndex} +\beta_3*\text{freq} + \beta_4*\text{amp}$

>>>>

|    Stiffness Model Predictors    |        Damping Model Predictors                     
|:---------------------------------|:------------------------------------|
           chemIndex               |             chemIndex
             freq                  |               freq
          log(cycle)               |            log(cycle)
              amp                  |             porosity
       chemIndex:log(cycle)        |         chemIndex:log(cycle)
        freq:log(cycle)            |           freq:log(cycle)
        amp:log(cycle)             |         porosity:log(cycle)

@@

Level 1: $\log(\text{stiffnessFrac}) = \alpha_i + \beta_i*log(cycle)$
Level 2: $\alpha_i = \alpha_0 + \alpha_1*\text{chemIndex} + \alpha_2*\text{freq} + \alpha_3*\text{amp}$
         $\beta_i = \beta_0 + \beta_1*\text{chemIndex} +\beta_2*\text{freq} + \beta_3*\text{amp}$
